---
title: "MP2 Technical Report: "
author: "Katy Cummings, Tulip Daaboul, Michel Ruiz-Fuentes"
format: pdf
editor: visual
  markdown: 
    wrap: 72
date: "`r Sys.Date()`"
indent: true
---

## Introduction

## Methodology

Our project's experimental units consisted of thirty-five Smith College students. We collected participants using a convenience sample, as those who took the survey came majority from our Research Design and Analysis class, other classes, and some of our student organizations on campus. Because the respondents came from a very specific demographic, we cannot generalize results to the Smith population. If random sampling was used, then, we would have been able to generalize to Smithies. 

However, we used random assignment when assigning the treatments to our participants, making our project an experiment. Our two treatments were Milk Type and Advertisement type. Participants were first assigned to either receive a dairy or plant based milk photo. Then, random assignment was used again and participants either received positive remarks with their assigned photo, negative remarks, or no remarks at all and just the photo (which acted as the control). 

The independent variables (experimental factors) in our study were the two treatments, milk type and advertisement type which were both categorical. The dependent variable was average consumption, which is continuous. After seeing their treatment, participants rated on an ordinal scale from 1-5 (1 being least likely, 5 being most likely) on how many times a week they consume the type of milk they were shown. For our study, we are going to be using a two way ANOVA model to see if there is a true difference in average consumption based on ad contents and sentiment types. 

## Results

[**Load Data:**]{.underline}

```{r, LOADPKGE, warning=F, message=F, echo=FALSE}
library(tidyverse)
library(rio)
library(asbio)
library(dplyr)
library(ggplot2)
library(Stat2Data)
library(car)

milk_df1 <- import("milk_cleaned_data.csv")

milk_df1$milk_type <- as.factor(milk_df1$milk_type)
milk_df1$ad_type <- as.factor(milk_df1$ad_type)
milk_df1$treatment <- as.factor(milk_df1$treatment)
```

[**Condition Check 1 Symmetrical Distribution around Group Means**]{.underline}:

We will compare the variation in the interquartile ranges of each `treatment`. This plot demonstrates that our distribution across the six groups are not equally distributed and violate our constant variance condition.

```{r, CONDI02, warning=F, message=F, fig.height = 3, fig.width = 6, fig.align = "center", echo=FALSE}
#BOX PLOT (constant variance)
milk_means <-
  ggplot(data=milk_df1, aes(x=average_consumption, y=treatment)) + 
  geom_boxplot(fill="steelblue3") + 
  stat_summary(fun="mean") + 
  labs(title ="Consumer Likelihood Box Plot",
      subtitle= "Assessing Distribution by Treatment",
      caption ="source: Qualtrics Milk Data") +
  xlab("Average Consumption") +
  ylab ("Treatment") + coord_flip()
milk_means

```

The box-plot above shows us the distribution of the average consumption on the different treatments. By looking at the plot, we can see that the constant variance condition is violated. We see that we do not have constant variance across groups and that the spread is not normal. However, checking conditions with visualizations can be tricky, so we can refer to levene's test to check our constant variance condition.

[**Levene's Test:**]{.underline}

```{r, LEVENET, warning=F, message=F, echo=FALSE}
leveneTest(average_consumption~treatment, data=milk_df1)
```

After condicting Levene's test of homogeneity of variance, we see that our p-value of 0.5326 is greater than 0.05. This means that we do not have statistically significant evidence that we have different variances.

[**Condition Check 2 Additive Effects & Transformation**]{.underline}:

```{r, CONDI03, warning=F, message=F, fig.height = 3, fig.width = 6, fig.align = "center", echo=FALSE}
TukeyNonaddPlot (average_consumption ~ ad_type + milk_type, data=milk_df1)
```

The Tukey Non-Additivity plot model helps us understand the relationship between the affect of both treatments over what we predicted. It also allows us to assess if the affects of treatments are additive or if there is some interaction. We want to relationship between the x-axis and y-axis to have a slope of 0 to indicate there is no relationship. However, because the data violates several assumptions and the slope is 2.7, so we must transform the data.

To diagnose the type of transformation we subtract 1-slope or 1-2.7 which gives the difference of -1.7. Because our P=-1.7, we must use a reciprocals transformation of 1/y.

```{r, INTERPRET, warning=F, message=F, echo=FALSE}
#RECIPROCAL TRANSFORMATION
milk_df1$average_consumption_transformed <- (1/milk_df1$average_consumption)
```

```{r, TUKEY2, warning=F, message=F, echo=FALSE}
TukeyNonaddPlot (average_consumption_transformed ~ ad_type + milk_type, data=milk_df1)
```

After transforming our data, we see that although we are getting closer to that slope of 0, we are not quite there yet. This means that an interaction might still be better for this model.

[**Two-Way ANOVA Model**]{.underline}:

```{r, MOD01, warning=F, message=F, echo=FALSE}
milk_anova <- aov(average_consumption~ad_type*milk_type, data=milk_df1) 
summary(milk_anova) 
```

The interaction model above shows us whether we have main effects for ad type, milk type, and if we have an interaction present.

Because our p-value for ad_type is 0.609 (greater than 0.05), we do not have statistically significant evidence that average consumption is different based on ad type. We do not have a main effect for ad type.

Because our p-value for milk_type is 0.686 (greater than 0.05), we do not have statistically significant evidence that average consumption is different based on milk type. We do not have a main effect for milk type.

[**Independent residuals:**]{.underline}

```{r, RESVFIT, warning=F, message=F, fig.height = 3, fig.width = 6, fig.align = "center", echo=FALSE}
plot(milk_anova, which = 1)
```

The residuals versus fitted plot can help us asses two patterns: non-linearity and non-constant spread. Because we see our residuals evenly spread out, we can say that our spread is constant. However, because our line does not fall on zero, non linearity is present here.

```{r, RESVFIT, warning=F, message=F, fig.height = 3, fig.width = 6, fig.align = "center", echo=FALSE}
plot(milk_anova, which = 2)
```

We can use this normal qquantile plot compares the standardized observed residuals with theoretical values from a normal distribution. This plot can help us determine whether our distribution is normal. Because we see that the residuals do not fall on the line, our distribution is not normal.

[**Confidence Intervals & Effect Size**]{.underline}:

```{r, TUKEY, warning=F, message=F, echo=FALSE}
#TUKEYHSD()
milk_tukey <- TukeyHSD(milk_anova)
milk_tukey
```

```{r, LSD, warning=F, message=F, echo=FALSE}
#FISHERSLSD
milk_lsd <-
  pairw.anova(milk_df1$average_consumption, 
              interaction(milk_df1$milk_type,milk_df1$ad_type),
              method="lsd", 
              conf.level=.95)
milk_lsd
```

```{r, BON, warning=F, message=F, echo=FALSE}
#BONFERONNI
milk_bonf <- 
  bonfCI(milk_df1$average_consumption, 
         interaction(milk_df1$milk_type,milk_df1$ad_type),
         conf.level = 0.95)

milk_bonf
```

```{r, EFFECTSIZE, warning=F, message=F, echo=FALSE}
#TREATMENT GROUP STATS
milk_summary <- 
  milk_df1 |>
  group_by(treatment) |>
  summarise(group_mean=mean(average_consumption), 
            group_n=n(), 
            group_sd=sd(average_consumption),
            group_min= min(average_consumption),
            group_max= max(average_consumption))  
milk_summary
```

[**R-Squared:**]{.underline}

we can get our r-squared from our anova

## Conclusion
