---
title: "MP2 Technical Report: "
author: "Katy Cummings, Tulip Daaboul, Michel Ruiz-Fuentes"
format: pdf
editor: visual
  markdown: 
    wrap: 72
date: "`r Sys.Date()`"
indent: true
---

## Introduction

## Methodology

## Results

[**Load Data:**]{.underline}

```{r, LOADPKGE, warning=F, message=F, echo=FALSE}
library(tidyverse)
library(rio)
library(asbio)
library(dplyr)
library(ggplot2)
library(Stat2Data)

milk_df1 <- import("milk_cleaned_data.csv")

```

[**Descriptive Statistics**]{.underline}:

```{r, SUMMARYSTATS, warning=F, message=F, echo=FALSE}
#TREATMENT GROUP STATS
milk_summary <- 
  milk_df1 |>
  group_by(treatment) |>
  summarise(group_mean=mean(average_consumption), 
            group_n=n(), 
            group_sd=sd(consumer_likelihood),
            group_min= min(consumer_likelihood),
            group_max= max(consumer_likelihood))  
milk_summary
```

[**Condition Check 1 Variability & Standard Deviation**]{.underline}:

Our largest standard deviation \[`Plant Control & Dairy Control`\] 1.38 divided by the smallest standard deviation \[`DairyCon(-)`\] 1.05 equals 1.31. Their quotient is smaller than 2, so we do not violate the condition about constant variance for our ANOVA model.

```{r, CONDI01, warning=F, message=F, echo=FALSE}
#STANDARD DEVIATION (constant variance)
1.38/1.05
```

[**Condition Check 2 Symmetrical Distribution around Group Means**]{.underline}:

We will compare the variation in the interquartile ranges of each `treatment`. This plot demonstrates that our distribution across the six groups are not equally distributed and violate our constant variance condition.

```{r, CONDI02, warning=F, message=F, fig.height = 3, fig.width = 6, fig.align = "center", echo=FALSE}
#BOX PLOT (constant variance)
milk_means <-
  ggplot(data=milk_df1, aes(x=average_consumption, y=treatment)) + 
  geom_boxplot(fill="darkseagreen3") + 
  stat_summary(fun="mean") + 
  labs(title ="Consumer Likelihood Box Plot",
      subtitle= "Assessing Distribution by Treatment",
      caption ="source: Qualtrics Milk Data") +
  xlab("Treatment") +
  ylab ("Average Purchase") + coord_flip()
milk_means
```

[**Condition Check 3 Additive Effects & Transformation**]{.underline}:

The Tukey Non-Additivity plot model helps us understand the relationship between the affect of both treatments over what we predicted. It also allows us to assess if the affects of treatments are additive or if there is some interaction. We want to relationship between the x-axis and y-axis to have a slope of 0 to indicate there is no relationship. However, because the data violates several assumptions and the slope is 2.7, so we must transform the data.

To diagnose the type of transformation we subtract 1-slope or 1-2.7 which gives the difference of -1.7. Because our P=-1.7, we must use a reciprocals transformation of 1/y.

```{r, CONDI03, warning=F, message=F, fig.height = 3, fig.width = 6, fig.align = "center", echo=FALSE}
TukeyNonaddPlot (average_consumption ~ ad_type + milk_type, data=milk_df1)
```

```{r, INTERPRET, warning=F, message=F, echo=FALSE}
#LOG TRANSFORMATION
log_milk <- 
  milk_df1 |>
  group_by(treatment) |>
  summarise(1/milk_df1$average_consumption)
#CALCULATING INTERCEPT
log_quant <- lm(log_sd~log_mean, data=log_milk)
log_quant
```

[**Two-Way ANOVA Model**]{.underline}:

```{r, MOD01, warning=F, message=F, echo=FALSE}
# milk_anova <- aov(consumer_likelihood~treatment, data=milk_df1) 
# summary(milk_anova) 

milk_anova2 <- aov(average_consumption~ad_type+milk_type, data=milk_df1) 
summary(milk_anova2) 
```

[**Interaction Model**]{.underline}:

```{r, MOD02, warning=F, message=F, echo=FALSE}

interaction <- aov(average_consumption~ad_type*milk_type, data=milk_df1) 
summary(interaction) 
```

[**Pairwise Comparison**]{.underline}:

```{r, PAIRWISE, warning=F, message=F, echo=FALSE}
#FISHERSLSD
milk_lsd <-
  pairw.anova(milk_df1$ad_type, 
              milk_df1$milk_type,
              method="lsd", conf.level=.95)
milk_lsd

#TUKEYHSD()
milk_tukey <- TukeyHSD(milk_anova2)
milk_tukey

#BONFERONNI
milk_bonf <- 
  bonfCI(milk_df1$consumer_likelihood, 
         milk_df1$ad_type, milk_df1$milk_type, 
         conf.level = 0.95)
milk_bonf
```

[**Independent residuals:**]{.underline}

```{r, RESIDCHECK01, warning=F, message=F, echo=FALSE}
# resid <-  resid(milk_anova)
# Model <- data.frame(Fitted = fitted(milk_anova), 
#                     Residuals = resid(milk_anova), 
#                     Treatment = milk_df1$treatment,
#                     Observed= milk_df1$consumer_likelihood)

resid2 <-  resid(milk_anova2)
Model2 <- data.frame(Fitted = fitted(milk_anova2), 
                    Residuals = resid(milk_anova2), 
                    Treatment = milk_df1$treatment,
                    Observed= milk_df1$consumer_likelihood)
```

```{r, RESIDPLOT01, warning=F, message=F, fig.height = 3, fig.width = 6, fig.align = "center", echo=FALSE}
#RESID PLOT
milk_resid <- 
  ggplot(Model2, aes(x = Fitted, y = Residuals)) +
  geom_point() +
  geom_hline(yintercept = 0) + 
  labs(title ="Fitted vs Residuals Residual Plot",
      subtitle= "Assessing Distribution by Treatment",
      caption ="source: Qualtrics Milk Data") 
milk_resid
```

[**Normally Distributed Residuals**:]{.underline}

In our density plot, we view the distribution of the `Consumer Likelihood` at the different levels of the `Milk (ad type and sentiment)` treatment. The data is not normally distributed nor unimodal among all levels. While the data distributions for the `Plant_control` and `PlantPro(+)` are normal, the other distributions vary. For example, `DairyCon` and `Plant_control` is bimodal, `Dairy control` and `DairyPro` is right-skewed. Therefore, we have violated the condition about constant variance for our ANOVA model.

```{r, RESIDCHECK02, warning=F, message=F, echo=FALSE}
#RESID PLOT2
milk_resid2 <-
  ggplot(data=Model2, aes(x=Residuals, color=Treatment)) + 
  geom_density() + 
  labs(title ="Treatment vs Residuals Density Plot",
      subtitle= "Assessing Distribution by Treatment",
      caption ="source: Qualtrics Milk Data") 
milk_resid2
```

[**Levene's Test:**]{.underline}

```{r, LEVENET, warning=F, message=F, echo=FALSE}
leveneTest(consumer_likelihood~treatment, data=milk_df1)
```

[**Confidence Intervals & Effect Size**]{.underline}:

```{r, CI, warning=F, message=F, echo=FALSE}
```

[**R-Squared:**]{.underline}

```{r, RSQUARED, warning=F, message=F, echo=FALSE}
```

## Conclusion
